Methods to prioritise pop-up active transport infrastructure

### 2020-06-19 article.Rmd
Update geographic subsetting section

```{r load}
library(sf)
library(tidyverse)
library(tmap)
region_name = "West Yorkshire"
# source("code/build.R")
# saveRDS(r_main_region, "r_main_region.Rds")
# r_main_leeds = r_main_region[region, ]
# saveRDS(r_main_leeds, "r_main_leeds.Rds")
# piggyback::pb_upload("r_main_leeds.Rds")
if(!file.exists("r_main_leeds.Rds")) {
  u = "https://github.com/cyipt/popupCycleways/releases/download/v1/r_main_leeds.Rds"
  download.file(u, "r_main_leeds.Rds")
}
rj = readRDS("r_main_leeds.Rds")
# r_lanes_joined = r_lanes_joined[region, ]
# saveRDS(r_lanes_joined, "r_lanes_joined.Rds")
# piggyback::pb_upload("r_lanes_joined.Rds")
if(!file.exists("r_lanes_joined.Rds")) {
  u = "https://github.com/cyipt/popupCycleways/releases/download/v1/r_lanes_joined.Rds"
  download.file(u, "r_lanes_joined.Rds")
}
r_lanes_joined = readRDS("r_lanes_joined.Rds")
region = ukboundaries::leeds
tmap_mode("plot")
```

```{r parameters}
regexclude = "welling"
min_cycling_potential = 0
min_grouped_cycling_potential = 50
min_grouped_length = 500
city_centre_buffer_radius_small = 5000
city_centre_buffer_radius = 8000
city_centre_buffer_radius_large = 10000
city_centre = tmaptools::geocode_OSM("leeds", as.sf = TRUE)
city_centre_buffer_small = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_small)
city_centre_buffer = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius)
city_centre_buffer_large = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_large)
hsf = readRDS(url("https://github.com/cyipt/popupCycleways/releases/download/0.1/acute_hospitals.Rds"))
h_leeds = hsf[city_centre_buffer, ]
h_leeds_buffer = stplanr::geo_buffer(h_leeds, dist = key_destination_buffer_radius)
city_key_buffer = st_union(city_centre_buffer, st_union(h_leeds_buffer))
```

@@

```{r gsub, fig.cap="Illustration of geographic subsetting based on distance to a central point (Leeds city centre in this case) rather than based on location within somewhat arbitrarily shaped city boundaries. Radii of 5 km, 8 km and 10 km are shown for reference (note that some roads within 10 km of the center are outside the regional boundary)."}
# nrow(r_central)
# nrow(rj)
square = stplanr::geo_bb(shp = city_centre_buffer)
r_main_region_key = r_main_region[city_key_buffer, ]
m1 = tm_shape(r_main_region) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(region) + tm_borders(col = "black", lwd = 2) +
  tm_shape(square) + tm_borders(lty = 3) +
  tm_scale_bar() 
# m1
m2 = tm_shape(r_main) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(city_centre_buffer_small) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_large) + tm_borders(lty = 2) +
  tm_shape(region) + tm_borders(col = "black", lwd = 2) +
  tm_shape(city_centre_buffer) + tm_borders() +
  tm_scale_bar() +
  tm_layout(legend.show = FALSE)
m3 = tm_shape(r_main_region_key) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(city_centre_buffer) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_small) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_large) + tm_borders(lty = 2) +
  tm_shape(city_key_buffer) + tm_borders() +
  tm_shape(h_leeds) + tm_dots(size = 0.5) +
  tm_scale_bar() +
  tm_layout(legend.show = FALSE)
# this take aaaages to render...
tmap_arrange(m1, m2, m3, nrow = 1)
```

>>>>

```{r load}
library(sf)
library(tidyverse)
library(tmap)
region_name = "West Yorkshire"
# source("code/build.R")
# saveRDS(r_main_region, "r_main_region.Rds")
# r_main_leeds = r_main_region[region, ]
# saveRDS(r_main_leeds, "r_main_leeds.Rds")
# piggyback::pb_upload("r_main_leeds.Rds")
if(!file.exists("r_main_leeds.Rds")) {
  u = "https://github.com/cyipt/popupCycleways/releases/download/v1/r_main_leeds.Rds"
  download.file(u, "r_main_leeds.Rds")
}
if(file.exists("r_main_region.Rds")) {
  rj = readRDS("r_main_region.Rds")
} else {
  rj = readRDS("r_main_leeds.Rds")
}
# r_lanes_joined = r_lanes_joined[region, ]
# saveRDS(r_lanes_joined, "r_lanes_joined.Rds")
# piggyback::pb_upload("r_lanes_joined.Rds")
if(!file.exists("r_lanes_joined.Rds")) {
  u = "https://github.com/cyipt/popupCycleways/releases/download/v1/r_lanes_joined.Rds"
  download.file(u, "r_lanes_joined.Rds")
}
r_lanes_joined = readRDS("r_lanes_joined.Rds")
region = ukboundaries::leeds
tmap_mode("plot")
```

```{r parameters}
regexclude = "welling"
min_cycling_potential = 0
min_grouped_cycling_potential = 50
min_grouped_length = 500
city_centre_buffer_radius_small = 5000
city_centre_buffer_radius = 8000
city_centre_buffer_radius_large = 10000
key_destination_buffer_radius = 5000
city_centre = tmaptools::geocode_OSM("leeds", as.sf = TRUE)
city_centre_buffer_small = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_small)
city_centre_buffer = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius)
city_centre_buffer_large = stplanr::geo_buffer(city_centre, dist = city_centre_buffer_radius_large)
hsf = readRDS(url("https://github.com/cyipt/popupCycleways/releases/download/0.1/acute_hospitals.Rds"))
h_leeds = hsf[city_centre_buffer, ]
h_leeds_buffer = stplanr::geo_buffer(h_leeds, dist = key_destination_buffer_radius)
city_key_buffer = st_union(city_centre_buffer, st_union(h_leeds_buffer))
```

@@

```{r gsub, fig.cap="Illustration of geographic subsetting based on distance to a central point (Leeds city centre in this case) rather than based on location within somewhat arbitrarily shaped city boundaries. Radii of 5 km, 8 km and 10 km are shown for reference (note that some roads within 10 km of the center are outside the regional boundary)."}
# nrow(r_central)
# nrow(rj)
square = stplanr::geo_bb(shp = city_centre_buffer)
r_main_region_key = r_main_region[city_key_buffer, ]
r_main_city = r_main_region[region, ]
m1 = tm_shape(r_main_city) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(region) + tm_borders(col = "black", lwd = 2) +
  tm_shape(square) + tm_borders(lty = 3) +
  tm_scale_bar() 
# m1
m2 = tm_shape(r_main) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(city_centre_buffer_small) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_large) + tm_borders(lty = 2) +
  tm_shape(region) + tm_borders(col = "black", lwd = 2) +
  tm_shape(city_centre_buffer) + tm_borders() +
  tm_scale_bar() +
  tm_layout(legend.show = FALSE)
m3 = tm_shape(r_main_region_key) +
  tm_lines("maxspeed", palette = "-Set1", lwd = "n_lanes_numeric", scale = 5,
           lwd.legend = c(1, 2, 3, 4, 5, 6), title.lwd = "Number of lanes") +
  tm_shape(city_centre_buffer) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_small) + tm_borders(lty = 2) +
  tm_shape(city_centre_buffer_large) + tm_borders(lty = 2) +
  tm_shape(city_key_buffer) + tm_borders() +
  tm_shape(region) + tm_borders(col = "black", lwd = 2) +
  tm_shape(h_leeds) + tm_dots(size = 0.5) +
  tm_scale_bar() +
  tm_layout(legend.show = FALSE)
# this take aaaages to render...
tmap_arrange(m1, m2, m3, nrow = 1)
```
